The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-06 paper/ms.tex
typos

We compare the solutions found using this set of fitting parameter with those found using only spectroscopic input in Figure~\ref{masses}, and we find that the change in median stellar parameters between the two results is small for all analyzed red giants. However, in the comparison plot it becomes clear that adding the asteroseismic constraints to the fit reduces the posterior uncertainty in stellar mass.

@@

In four of the five targets we found evidence for binarity, while in the fifth (HD\,185397) there was some time-delay variation but there was no agreement between different modes so it is not of binary origin. Of the others, HD\,175841 and HD\,177781 are probably very long-period binaries, with periods far exceeding the Kepler datasets of $\sim$1470\,d. HD\,181521 appears to be an eccentric binary with a period of at least 1000\,d, but there is only 1 maximum and 1 minimum in the time-delay curve (\citep[cf.][]{murphy&shibahashi2015}), so a unique orbital solution was unobtainable. Finally, HD\,186255 is probably a binary with a period of $\sim$415\,d (Figure~\ref{pm}), but there is a slight aperiodicity in the time delays, likely caused by beating between pulsation modes that are not well-separated in the frequency. That, coupled with the fact that this star falls on the failed Module 3 and is therefore missing data every 4th quarter (i.e. $\sim$93 of every 372.5\,d), makes the binary classification uncertain. If this is indeed a 415-d binary, the time delays are consistent with a companion of minimum mass $\sim$0.45\,M$_{\odot}$ in an orbit of moderate eccentricity ($\sim$0.15).

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. B.P. also acknowledges support from Balliol College and the Clarendon Fund. D.H. acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC18K0362) and the National Science Foundation (AST-1717000). DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory. The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No670519: MAMSIE). V.S.A. acknowledges support the Independent Research Fund Denmark (Research grant 7027-00096B). Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement No.~DNRF106). PJ acknowledges FONDECYT Iniciaci\'on grant 11170174.

BP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples. We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands. We would like to acknowledge the Gadigal Clan of the Eora Nation as the traditional owners of the land on which the University of Sydney is built and on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.

>>>>

We compare the solutions found using this set of fitting parameters with those found using only asteroseismic input in Figure~\ref{masses}, and we find that the change in median stellar parameters between the two results is small for all analyzed red giants. However, in the comparison plot it becomes clear that adding the spectroscopic constraints to the fit reduces the posterior uncertainty in stellar mass.

@@

In four of the five targets we found evidence for binarity, while in the fifth (HD\,185397) there was some time-delay variation but there was no agreement between different modes so it is not of binary origin. Of the others, HD\,175841 and HD\,177781 are probably very long-period binaries, with periods far exceeding the Kepler datasets of $\sim$1470\,d. HD\,181521 appears to be an eccentric binary with a period of at least 1000\,d, but there is only 1 maximum and 1 minimum in the time-delay curve \citep[cf.][]{murphy&shibahashi2015}, so a unique orbital solution was unobtainable. Finally, HD\,186255 is probably a binary with a period of $\sim$415\,d (Figure~\ref{pm}), but there is a slight aperiodicity in the time delays, likely caused by beating between pulsation modes that are not well-separated in the frequency. That, coupled with the fact that this star falls on the failed Module 3 and is therefore missing data every 4th quarter (i.e. $\sim$93 of every 372.5\,d), makes the binary classification uncertain. If this is indeed a 415-d binary, the time delays are consistent with a companion of minimum mass $\sim$0.45\,M$_{\odot}$ in an orbit of moderate eccentricity ($\sim$0.15).

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. BJSP also acknowledges support from Balliol College and the Clarendon Fund. DH acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC18K0362) and the National Science Foundation (AST-1717000). TRW acknowledges the support of the Australian Research Council (grant DP150100250). DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory. The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No670519: MAMSIE). VSA acknowledges support the Independent Research Fund Denmark (Research grant 7027-00096B). Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement No.~DNRF106). PJ acknowledges FONDECYT Iniciaci\'on grant 11170174.

BJSP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples. We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands. We would like to acknowledge the Gadigal Clan of the Eora Nation as the traditional owners of the land on which the University of Sydney is built and on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.
